---
title: "Invisibility cloak analysis"
author: "Mark Lescroart"
date: "3/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a demo analysis of the (made up) invisibility cloak data. This code file should live within a folder called lab_06_R_dplyr/ on your computer. The full file structure should be: 

```
lab_06_R_dplyr/
├── code
│   └── invisibility_cloak_analysis.Rmd
├── data
│   ├── invisibility_cloak_btw_subj.xlsx
│   ├── invisibility_cloak_within_subj.xlsx
│   └── posner_cueing.2021-03-04-0524.data.e2679654-e2a8-4c32-a046-fbfe32992006.txt
├── figures
└── lab_06_R_dplyr.Rproj
```

To run this code, you should have opened `lab_06_R_dplyr.Rproj` with RStudio.

In order for this demo to run correctly, you will need to install the tidyverse package for RStudio (if you haven't already). This just means calling the following line at a terminal:

`install.packages(tidyverse)`

Here we go with the demo!

```{r libraries}
# Get useful libraries
library(dplyr)
library(readxl)
```

Here is the loading of the data. 

```{r loading}
data_btw <- readxl::read_excel('../data/invisibility_cloak_btw_subj.xlsx')
data_within <- readxl::read_excel('../data/invisibility_cloak_within_subj.xlsx')

#View(data_btw)
#View(data_within)
```

Next, we will use functions from the dplyr library to compute the means by condition. 

```{r analysis}
cond_means_btw = data_btw %>% 
  group_by(condition) %>% 
  summarize(grp_means=mean(n_mischief), n_participants=n())

cond_means_within = data_within %>% 
  group_by(condition) %>% 
  summarize(grp_means=mean(n_mischief), n_participants=n())

#View(cond_means_within)

barplot(cond_means_within$grp_means, names.arg = cond_means_within$condition, ylab = 'Mean acts of mischief', main= 'Within Subject Design')

barplot(cond_means_btw$grp_means, names.arg = cond_means_btw$condition, ylab = 'Mean acts of mischief', main= 'Between Subject Design')


```

